Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-05-07 research_proposal/research_proposal_draft.qmd
small fixes and re render

@Wickramasuriya2019-xq also showed that MinT is an algebraical generalisation of the GLS, and the OLS and WLS methods are special cases of MinT when $\boldsymbol{W}_h$ is an identity and a diagonal matrix, respectively. However, the MinT solution hinges on a reliable estimate of $\boldsymbol{W}_h$, which is challenging to estimate in high-dimensional setting. Therefore, we will be exploring alternative covariance estimators.

@@

$$
\hat{\lambda}_D = \frac{\sum_{i \neq j} \widehat{Var}(\hat{r}_{ij})} {\sum_{i \neq j} \hat{r}_{ij}}
$$

>>>>

@Wickramasuriya2019-xq also showed that MinT is an algebraic generalisation of the GLS, and the OLS and WLS methods are special cases of MinT when $\boldsymbol{W}_h$ is an identity and a diagonal matrix, respectively.

The MinT solution hinges on a reliable, positive-definite estimate of $\boldsymbol{W}_h$, which is challenging to estimate in high-dimensional setting. Therefore, we will be exploring alternative covariance estimators.

@@

$$
\hat{\lambda}_D = \frac{\sum_{i \neq j} \widehat{Var}(\hat{r}_{ij})} 
{\sum_{i \neq j} \hat{r}_{ij}^2}
$$
